---
title: "Analysis of Unicorn Companies in Top 10 Countries"
author: "Raynard Widjaja"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning=FALSE)
library(tidyverse)
library(lubridate)
```

```{r data_process}
unicorn <- read_csv("unicorns.csv", show_col_types = FALSE) %>%
  select(-1) %>%
  mutate(`Valuation ($B)` = as.numeric(substr(`Valuation ($B)`, 2, nchar(`Valuation ($B)`)))) %>%
  rename(Valuation = `Valuation ($B)`) %>%
  mutate(`Date Joined` = as.Date(`Date Joined`, format = "%m/%d/%Y")) %>%
  mutate(year = year(`Date Joined`)) %>%
  mutate(month = month(`Date Joined`))
  
country <- read_csv("Country_Data.csv", show_col_types = FALSE)

num_country <- unicorn %>% 
  group_by(Country) %>% 
  summarize(num_unicorn = n(), valuation=sum(Valuation))

top_num_unicorn <- country %>%
  left_join(num_country, by=join_by(country==Country)) %>%
  arrange(desc(num_unicorn)) %>%
  slice(1:10)

uni_country <- unicorn %>%
  group_by(Country, Industry) %>%
  summarize(num_industry = n()) %>%
  left_join(country, by=join_by(Country==country)) %>%
  left_join(num_country, by=join_by(Country==Country)) %>%
  filter(Country %in% c("Brazil", "Canada", "China", "France", "Germany", "India", "Israel", "Singapore", "United Kingdom", "United States"))
```

## How does the total valuation and the average valuation of unicorn companies in the US compare to other countries ?

```{r plot1.1}
# Total valuation of Unicorn per country (Top 10)
ggplot(data=top_num_unicorn) + 
  geom_col(aes(x=valuation, y=country)) +
  labs(x = "Total Valuation ($B)", y = "Country")
```
Title: Total valuation of unicorn companies in top 10 countries

In terms of total valuation, the US stands out as the leader among the top 10 countries, boasting over $2 trillion USD, nearly quadrupling China's total. This dominance is attributed to the robust funding environment and innovation capacity within the US. With its abundance of venture capital, entrepreneurs in the US can pursue projects with financial backing, supported by a strong educational system that cultivates skilled professionals and fosters knowledge exchange hubs like the Bay Area and Silicon Valley, driving experimentation and solution discovery. The phenomenon of a "Unicorn Bubble" may also contribute to the inflated valuations, fueled by overvaluation by venture capitalists or investors, especially during private funding rounds or IPOs. With over 400,000 new startups annually, the US is particularly susceptible to and instrumental in driving the startup bubble.

```{r plot1.2}
# Average valuation of Unicorn per country (Top 10)
ggplot(data=top_num_unicorn) + 
  geom_col(aes(x=valuation/num_unicorn, y=country)) +
  labs(x = "Average Valuation ($B)", y = "Country")
```
Title: Average valuation of unicorn companies in top 10 countries

Surprisingly, Singapore emerges as the leader in average unicorn valuation among the top 10 countries, exceeding $5 billion USD, with the US notably absent from the top three. Several factors could explain this discrepancy. While the US may have a higher quantity of unicorns, their individual valuations might be lower, leading to a lower average. Additionally, Singapore's conducive regulatory environment, streamlined bureaucracy, favorable tax policies, robust infrastructure, and highly productive workforce attract unicorn investments, reflecting an investor-friendly ecosystem. The proliferation of unicorn companies in Singapore underscores its appeal as an investment destination, driven by promising growth prospects and anticipated gains in potential buyouts.


## Does higher GDP per capita mean more unicorn companies ?
```{r plot2}
# Correlation of GDP and Number of Unicorn
ggplot(data=top_num_unicorn) + 
  geom_line(aes(x=gdpp, y=num_unicorn)) +
  geom_point(aes(x=gdpp, y=num_unicorn, color=country)) +
  labs(x = "GDP per Capita", y = "Number of Unicorn")
```
Title: Relationship Between GDP per Capita and Unicorn Company Presence

Countries with higher GDP per capita typically exhibit superior infrastructure, longer life expectancies, increased funding opportunities, and enhanced educational quality, resulting in a more skilled workforce. This trend is evident in the correlation between GDP per capita and the number of unicorn companies. For instance, the US, boasting a high GDP per capita, also hosts a substantial number of unicorn companies. Conversely, established European nations like France, Germany, and the United Kingdom lag behind in unicorn company count, possibly due to stringent regulations imposed by the European Parliament, such as those pertaining to business startup, minimum wage, and data privacy, leading to bureaucratic hurdles.

However, a notable anomaly emerges when comparing countries like India and China to their European counterparts. Despite having lower GDP per capita, India and China exhibit a significantly higher number of unicorn companies. This can be attributed to robust government support in both countries, incentivizing technological innovation and increasing venture capital investment. Moreover, the abundance of skilled yet cost-effective labor in these populous nations contributes significantly to their startup ecosystem's success.


## Comparative Analysis of Unicorn Company Industries in Countries with Varying GDP per Capita

```{r plot3}
# Average Num of Unicorn and GDP and Industries
ggplot(data=uni_country) + 
  geom_point(aes(x=gdpp, y=num_industry/num_unicorn, color=Industry)) + 
  labs(x = "GDP per Capita", y = "Average Number of Unicorn")
```

Title : Comparison of the Industries of the Unicorn Companies in Country with Low and High GDP per Capita

A notable contrast exists in the distribution of unicorn company industries between countries with low and high GDP per capita. In nations with lower GDP per capita, unicorn companies are predominantly concentrated in consumer retail, industrial, and financial services sectors. Conversely, countries boasting higher GDP per capita predominantly host unicorn companies operating within the financial services and enterprise technology industries.


## About the Data

The two dataset utilized to address these research inquiries is provided by Kaggle. The unicorn dataset contain a complete list of unicorn companies in the world. A unicorn company, or unicorn startup, is a private company with a valuation over $1 billion. As of March 2022, there are 1,000 unicorns around the world. The country dataset provides a comprehensive view of various socioeconomic indicators across different countries. It includes data on child mortality rates, export and import figures, healthcare expenditures, income levels, inflation rates, life expectancy, fertility rates, and Gross Domestic Product (GDP). Analyzing this dataset can offer insights into the interplay between economic factors, public health, and demographic trends on a global scale. We can then further process the data by filtering only the top ten countries and join both of the dataset by the country.